\thetitle

### 2023-06-11 frontmatters.tex
Fix typo.

Ende Jin was the sole author for \cref{sec:complete-fmltt}, which were written under the supervision of Prof. Yizhou Zhang.

@@

\noindentparagraph{Research presented in rest of the thesis:}
The research was conducted at the University of Waterloo by Ende Jin under the supervision of Dr. Yizhou Zhang. Ende Jin proposed the primary design of the language, prototyped the Coq plugin for realizing the language, implemented and evaluated the case studies, and formalized and proved meta-theoretic arguments for the core type theory. Ende Jin estabilished the complete language design with consultations from Dr. Yizhou Zhang.

>>>>

Ende Jin was the sole author for \cref{sec:complete-fmltt}, which were written under the supervision of Dr. Yizhou Zhang.

@@

\noindentparagraph{Research presented in the rest of the thesis:}
The research was conducted at the University of Waterloo by Ende Jin under the supervision of Dr. Yizhou Zhang. Ende Jin proposed the primary design of the language, prototyped the Coq plugin for realizing the language, implemented and evaluated the case studies, and formalized and proved meta-theoretic arguments for the core type theory. Ende Jin estabilished the complete language design with consultations from Dr. Yizhou Zhang.
